Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add decrese in alpha plot

\subsection{Cause of $\alpha$ Decline}\label{ssec:sfe}
As discussed in Section~\ref{sec:intro}, it has long been known that the \alphaFe{} ratio should decline with time \red{cite}. This declination is caused by the relative enrichment contribution between Type II and Type Ia SNe, with the former contributing the bulk of the $\alpha$-elements and both contributing to Fe. However, this picture is complicated by the details of galaxy evolution. Inflows and outflows, radial gas transfer, and unmixed local enrichment all have a strong effect on the \alphaFe{} ratio.

A detailed accounting of all these processes is beyond the scope of this work, and much of it is impossible with the sparse snapshot spacing in TNG. However, we do offer one possible explanation for the relatively minor declination of \alphaFe{} in the simulation: the SFE at high surface densities in TNG is too low.

First, we demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}. The details of our setup is given in Section~\red{X}. We vary the star formation timescale, $\tau_{*}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time. We find that shorter star formation timescales lead to a more rapid reduction in \MgFe{}. A close match to our subhalo of interest in TNG is not attempted.

In TNG, the SF timescale is set to a fixed value of $2.2\,\Gyr$. However, this value is the SF timescale used to set the SFR of an individual cell. What is relevant for comparison to these models is the SF timescale averaged over some well-mixed region.

>>>>

\subsection{Steepening of $\alpha$ Decline}\label{ssec:sfe}
As described in Section~\ref{X}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation. Specifically, to star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time. This post-processed subhalo is presented alongside the fiducial subhalo in the right and middle columns, respectively, of Figures~\ref{fig:fig1} and \ref{fig:alpha}.

The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, and, of course, enrichment models. Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible. However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.

We demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}. The details of our setup is given in Section~\red{X}. We vary the star formation timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time. We find that shorter star formation timescales do lead to a more rapid reduction in \MgFe{}. We assumed an additional decrease rate of $0.1\,\dex/\Gyr$. Such a difference in the rate occurs between the $\tau_{\star}=0.5$ and $1\,\Gyr$ models at their respective maximum slope magnitudes.

In TNG, the SF timescale is set to a fixed value of $2.2\,\Gyr$. However, this value is the SF timescale used to set the SFR of an individual cell. What is relevant for comparison to these models is the SF timescale averaged over some well-mixed region. Hassan et al. (in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude, well within our needed factor of $2$ in $\tau_{\star}$.

Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
